---
title: "NCTs - Substory 1"
author: "Linh Dang"
format: html
editor: visual
---

# 1. Load Libraries and Data

```{r}
library(phyloseq)
library(microbiome)
library(taxizedb)
library(readxl)
library(dplyr)
library(pairwiseAdonis)
library(cowplot)
library(ggrepel)
library(grid)
library(tidyr)
#install.packages("remotes")
#remotes::install_github("david-barnett/microViz")
library(microViz)
##-----
my_cols <- c("#9d547c","#56ca63","#a357d6","cornflowerblue","#419d2a","sandybrown","red3","peachpuff","cyan","paleturquoise3","mistyrose","mediumpurple","mediumseagreen","mediumorchid","moccasin","orange4","olivedrab","midnightblue","papayawhip","palevioletred4","brown1","greenyellow","orchid","navy","darkred","navajowhite1","mistyrose1","grey85","#525fd6","red2","#8cbe3a","#c944aa","indianred3","#5ba557","#9e66cb","#c1b735","#6d82ec","grey25","#e69728","#6654b0","lightsalmon3","lightcyan1","khaki1","seagreen1","plum1","lightsteelblue1","palevioletred3","mintcream","magenta3","#799330","#da7fdf","#3c782c","#e44586","blue4","#63c996","#dc3f53","#49cbc8","#cf3f29","#4fabda","#da6c2b","#598bd1","#b78c24","#8d4191","#a0b971","slategray1","sienna","plum1","lightyellow1","lightskyblue3","linen","limegreen","cornsilk1","mediumaquamarine","gray14","gold3","darkviolet","#b2386a","#479d71","#ae4341","#2ba198","#e07557","#5361a3","#dda353","#aa98df","#5b6114","#dc89bf","#327243","slateblue1","#e57b94","#277257","#9b62a0","#bbab59","#98495a","#526229","#d8827d","#857624","gray40","#9a4a22","#7c7d46","mediumslateblue","lemonchiffon1","#e3a073","#9e6b33", "gray74","slateblue1","rosybrown3", "lawngreen","gainsboro","dodgerblue3","deeppink3","firebrick3", "orchid2", "olivedrab1", "ivory3", "darkseagreen", "bisque2", "darkgoldenrod2", "blue2", "skyblue", "seashell2", "turquoise", "tan1", "seagreen2", "palevioletred3", "linen", "steelblue4","ghostwhite","dodgerblue1","deeppink1","firebrick1", "limegreen", "purple3", "khaki3", "snow3", "darkslategray","darkorchid","lavender", "magenta2", "palegreen", "salmon", "maroon", "cyan2","#671408","#FAEBD7","#7FFFD4","#F0FFFF","#A52A2A","burlywood","cadetblue","#7FFF00","chocolate","cornsilk","slateblue1","#FF7F50","red1","#008B8B","darkgoldenrod1","darkolivegreen","darkorange4","white","hotpink","honeydew1","goldenrod2","darkgreen","oldlace","darkslategray3","navajowhite3","orchid4","gray25","#F0924D")
```

# Additional functions

```{r}
###----- Beta --------------
BetaPlot <- function(PhyloObjct, feature = "Treatment", title_method = "Original", dis_method = "bray", ordination_method = "PCoA"){
  bray_dist = phyloseq::distance(PhyloObjct, method=dis_method)
  ordination = ordinate(PhyloObjct, method=ordination_method, distance=bray_dist)

  pcoa1 <- paste("PCoA 1 [", round(ordination[[3]]$Relative_eig[1], digits = 3)*100, "%]", sep = "")
  pcoa2 <- paste("PCoA 2 [", round(ordination[[3]]$Relative_eig[2], digits = 3)*100, "%]", sep = "")

p.adonis <- adonis2(bray_dist ~ sample_data(PhyloObjct)[, feature][[1]])
p <- case_when(
  p.adonis$`Pr(>F)`[1] > 0.05 ~ paste("p =", p.adonis$`Pr(>F)`[1], "n.s.", sep = " "),
  p.adonis$`Pr(>F)`[1] < 0.05 &  p.adonis$`Pr(>F)`[1] > 0.01 ~ paste("p =", p.adonis$`Pr(>F)`[1], "*", sep = " "),
  p.adonis$`Pr(>F)`[1] <= 0.01 & p.adonis$`Pr(>F)`[1] > 0.001  ~ paste("p =", p.adonis$`Pr(>F)`[1], "**", sep = " "),
  p.adonis$`Pr(>F)`[1] <= 0.001 ~ paste("p =",p.adonis$`Pr(>F)`[1], "***", sep = " "),
)

annotations <- data.frame(
        xpos = c(-Inf),
        ypos =  c(Inf),
        annotateText = p,
        hjustvar = c(-0.2) ,
        vjustvar = c(1.5))

p1 <- plot_ordination(PhyloObjct, ordination, color = feature) +
  geom_point(aes_string(colour = feature), size = 3) +
  geom_text_repel(aes(label = id), size = 4) +
  theme(aspect.ratio=1) +
  theme_bw()+
  scale_color_brewer(palette = "Set1")+
  stat_ellipse() +
  xlab(pcoa1)+
  ylab(pcoa2)+
  theme(panel.grid =  element_blank())+
  ggtitle(paste0(title_method, " - Tumor gemcitabine")) +
  theme (axis.text=element_text(size=14),
         axis.title=element_text(size=16,face="bold"),
        legend.text = element_text(size = 12),
        legend.title = element_blank())+
  geom_text(data=annotations,aes(x=xpos,y=ypos,hjust=hjustvar,vjust=vjustvar,label=annotateText), size = 4.5, inherit.aes = FALSE)
return(p1)
}
### ---- compositional plot with annotation in x-axis
CompositionPlot <- function(PhyloseqObj, target_rank='order', rel_abundance=0.03){
  physeq.fam <- transform_sample_counts(PhyloseqObj, function(x){x/sum(x)})
  df.fam.melt <- psmelt(physeq.fam)
  if(tolower(target_rank)=='order'){
    df.fam.melt$target_rank <- ifelse(df.fam.melt$Abundance>rel_abundance,as.character(df.fam.melt$order), "others")
  } else if(tolower(target_rank)=='family'){
    df.fam.melt$target_rank <- ifelse(df.fam.melt$Abundance>rel_abundance,as.character(df.fam.melt$family), "others")
  } else if(tolower(target_rank)=='genus'){
    df.fam.melt$target_rank <- ifelse(df.fam.melt$Abundance>rel_abundance,as.character(df.fam.melt$genus), "others")
  } else if(tolower(target_rank)== 'species'){
    df.fam.melt$target_rank <- ifelse(df.fam.melt$Abundance>rel_abundance,as.character(df.fam.melt$species), "others")
  } else{
    stop("Unknown target rank. Must be one of the list: order, family, genus, species.")
  }
  
  df.fam.melt$target_rank <- factor(df.fam.melt$target_rank, levels=rev(unique(df.fam.melt$target_rank)))
  
## create sample annotation
  
  
plt1 <-  ggplot(df.fam.melt, aes(x=id, y=Abundance, fill=target_rank)) +
    geom_bar(stat="identity") +
    scale_y_continuous(labels = scales::percent, expand = c(0, 0), limits = c(0, 1.02)) +
    scale_fill_manual(values = cols) +
    xlab ("") +
    ylab("Relative abundance") +
    theme_bw() +
    ggtitle(paste0("Microbial composition at ",target_rank, " level"))+
    theme( axis.text.x = element_text(angle=45,  vjust = .5),
           axis.text.y = element_text (size=12),
           axis.title = element_text(size=14, face="bold"))+
    theme(legend.position = "bottom",
          legend.title = element_blank(),
          legend.background = element_rect(size=0.4, linetype="solid", colour ="black"),
          legend.key.size = unit(6,"mm")) 
return(plt1)
}
```

# Load and clean Object & Preprocess

```{r}
NCTs <- readRDS("./physeqs/combined_ntc_physeq_object.rds")
### replace NA person as Unknown
## only 16S
NCTs <- prune_samples(sample_data(NCTs)[, "seq_approach"][[1]] == "16S", NCTs)

## remove NCT sample if read count is less than a certain number
NCTs_RmLowReads <- phyloseq::prune_samples(sample_sums(NCTs)>=250, NCTs)
## remove extreme low abundance taxa (assumption: results from noise mapping)
NCT_RmLowAbun <- filter_by_low_abundance(NCTs_RmLowReads, 0.0001, 1)
rm(list = c("NCTs", "NCTs_RmLowReads"))

## tax glom
NCT_16S_Bac <- subset_taxa(NCT_RmLowAbun, superkingdom=="Bacteria")
NCT_16S_Bac <- tax_glom(NCT_16S_Bac, taxrank = "species", NArm = TRUE)
## filter taxa and sample
NCT_16S_Bac <- prune_samples(sample_sums(NCT_16S_Bac)>100, NCT_16S_Bac)
NCT_16S_Bac <- prune_taxa(taxa_sums(NCT_16S_Bac)>=5, NCT_16S_Bac)

## remove sample_type == seq_ctrl
NCT_16S_Bac <- prune_samples(sample_data(NCT_16S_Bac)$sample_type != "seq_ctrl", NCT_16S_Bac)
## change person NA to unknown
df_person <- sample_data(NCT_16S_Bac)$person
df_person_edit <- lapply(df_person, function(x){ifelse(is.na(x), "Unknown", x)}) %>% unlist()
sample_data(NCT_16S_Bac)$person <- df_person_edit
## save back
saveRDS(NCT_16S_Bac, "./physeqs/NCTs_16S_Bac.rds")
```

# 2. Load Eisenhofer List

What is the prevalence of well-known contaminants (from Eisenhofer et al. list) over time in this specific lab setting?

Import Eisenhofer list

```{r}
Eisenhofer_tab <- read_excel("./metadata/Eisenhofer_lst.xlsx")
## 
table( Eisenhofer_tab$genus %in% tax_table(NCT_RmLowAbun)[, "genus"])
tax_table(NCT_RmLowAbun)[, "genus"] %>% unique() %>% length()
```

Composition plot

```{r}
# p.prop <- microbiome::transform(NCT_RmLowAbun, "compositional") 
# df.fam.melt <- psmelt(p.prop) %>% 
#   mutate(species.v2 = if_else(
#     Abundance < 0.04, "other", species 
#    ),
#    species.v2 = factor(species.v2, levels=rev(unique(species.v2)))
#   ) 
# 
# rm(p.prop)
# 
# 
# #microbial composition at species level
# ggplot(df.fam.melt, aes(x=pseudonym, y=Abundance, fill=species.v2)) +
#   geom_bar(stat="identity") +
#   scale_y_continuous(labels = scales::percent, expand = c(0, 0), limits = c(0, 1.02)) +
#   scale_fill_manual(values = cols) +
#   xlab ("") +
#   ylab("Relative abundance") +
#   theme_bw() +
#   # facet_wrap(vars(Treatment), scales = "free_y") +
#   ggtitle("TRUE - Microbial composition at species level")+
#   # facet_wrap(~sample_side, scales = "free")+
#   theme( axis.text.x = element_text(angle = 45,hjust=1),
#         axis.text.y = element_text (size=12),
#         axis.title = element_text(size=14, face="bold"))+
#   theme(legend.position = "bottom",
#         legend.title = element_blank(),
#         legend.background = element_rect(linetype="solid", colour ="black"),
#         legend.key.size = unit(4,"mm"))
```

## 2.1 Composition barplots

```{r}
library(hrbrthemes)
library(gcookbook)

p <- NCT_16S_Bac %>%
  plot_composition(sample.sort = "year", otu.sort = "abundance") +
  # Set custom colors
  scale_fill_manual("Phylum",values = default_colors("Phylum")[taxa(NCT_16S_Bac)]) +
  scale_y_continuous(label = scales::percent) + 
  theme_ipsum(grid="Y") +
  # Removes sample names and ticks
  theme(axis.text.x=element_blank(), 
        axis.ticks.x=element_blank())
print(p)
```

3.  

    # 3. Batch Association

    ```{r}
    p <- BetaPlot(NCT_16S_Bac, feature = "sample_type")
    p
    ```

```{r}
## person
p_person <- BetaPlot(NCT_16S_Bac, feature = "person")
p_person
```

```{r}
p_year <- BetaPlot(NCT_16S_Bac, feature = "year")
p_year
```

Composition Analysis

```{r}
p_compo <- CompositionPlot(subset_samples(NCT_16S_Bac, year == "2024"), target_rank = "family")
print(p_compo)
```

# Visualize with MicroViz

```{r}
NCTs <- readRDS("./physeqs/NCTs_CorrectedTaxa_AdjustName.rds")
NCTs_genus <- tax_glom(NCTs, taxrank = "genus", NArm = TRUE)
pseq <- NCTs %>%  
  tax_fix(unknowns = c("uncultured")) %>% 
  phyloseq_validate()
ord_explore(pseq)
## modify Eisenhofer list
Eisenhofer_tab <- Eisenhofer_tab %>% 
  mutate(In_NCT = genus %in% tax_table(NCTs)[, "genus"])
```

```{r}
library(grid)
## pseq <- pseq %>%  tax_fix(unknowns = c("Candidatus", "[Clostridium]", "bacterium"))
pseq %>% 
  prune_samples(sample_data(.)[, "year"][[1]]=="2022", .) %>% 
  subset_taxa(genus %in% Eisenhofer_tab$genus) %>% 
  tax_transform(trans = "compositional", rank = "class") %>% 
  comp_heatmap(tax_anno = taxAnnotation(Prev. = anno_tax_prev(bar_width = 0.3, size = grid::unit(1, "cm"))),
               sample_anno = sampleAnnotation(
                 person = anno_sample("person"),
                 type = anno_sample("sample_type"),
                 border = FALSE
               ))
```

Only look at genus in Eisenhofer list

```{r}
pseq %>% 
  tax_transform(trans = "compositional", rank = "genus") %>% 
  subset_taxa(genus %in% Eisenhofer_tab$genus) %>% 
  prune_taxa(prevalence(., sort = F)>0.30, .) %>% 
  ##tax_to
  comp_heatmap( tax_anno = taxAnnotation(Prev. = anno_tax_prev(bar_width = 0.3, size = grid::unit(1, "cm"))),
               sample_anno = sampleAnnotation(
                 person = anno_sample_cat("person", col = cols[1:9], legend_title = "person"),
                 year = anno_sample_cat("year", col = cols[10:13], legend_title = "year"),
                 type = anno_sample_cat("sample_type", col = cols[13:15], legend_title = "type"),
                 border = FALSE
               )
               )
```

Only keep top 20 Taxa whose best median Rel Abundance

## Heatmap

```{r}
## sample order sorted by year
ps_byYear <- sample_names(pseq)[sample_data(pseq)$year %>% order()]  
pseq_byYear <- ps_reorder(pseq, ps_byYear)
## 20 most prevalence taxa at genus level
Most_prev_30_genus <- pseq %>% 
  tax_top(n=30, by = "prev", rank = "genus", undetected = 2)
Most_abun_30_genus <- pseq %>% 
  tax_top(n=30, by = sum, rank = "genus")
In_list <- Most_prev_30_genus %in% Eisenhofer_tab$genus 
pseq %>% 
  #ps_reorder(ps_byYear) %>% 
  ##subset_taxa(genus %in% Most_prev_30_genus) %>% 
  ## microViz::tax_mutate(InEisenhofer = ifelse(genus %in% Eisenhofer_tab$genus, "TRUE", "FALSE")) %>% 
  tax_transform(trans = "compositional", rank = "genus") %>% 
  comp_heatmap(
    #taxa = Most_prev_30_genus,
    taxa = Most_abun_30_genus,
    cluster_rows = FALSE, 
    cluster_columns = FALSE,
    row_title = NULL,
    ##facet_wrap()
    tax_anno = taxAnnotation(
      InList = ComplexHeatmap::anno_points(In_list, which = "row", gp= gpar(col = "red")),
      Prev. = anno_tax_prev(bar_width = 0.5, size = grid::unit(1, "cm"), border = F),
      Prop_Abd. = anno_tax_box(size = unit(2, "cm"))
      ),
    sample_anno = sampleAnnotation(
      year = anno_sample_cat("year", col = my_cols[1:4], legend_title = "year"),
      person = anno_sample_cat("person", col = my_cols[5:13], legend_title = "person"),
      type = anno_sample_cat("sample_type", col = my_cols[14:16], legend_title = "ctrl type")
    )
  ) %>% 
  ComplexHeatmap::draw(
  annotation_legend_list = attr(. , "AnnoLegends")
)
```

At species level

```{r}
### same as above but in species level

Most_prev_30_species <- pseq %>% 
  tax_top(n=30, by = "prev", rank = "species", undetected = 2)

In_list_species <- lapply(Most_prev_30_species, function(x){
  genus_name <- strsplit(x, "\\s+")[[1]][1]
  return(genus_name %in% Eisenhofer_tab$genus)
}) %>% unlist()
pseq %>% 
  #ps_reorder(ps_byYear) %>% 
  ##subset_taxa(genus %in% Most_prev_30_genus) %>% 
  ## microViz::tax_mutate(InEisenhofer = ifelse(genus %in% Eisenhofer_tab$genus, "TRUE", "FALSE")) %>% 
  tax_transform(trans = "compositional", rank = "species") %>% 
  comp_heatmap(
    taxa = Most_prev_30_species,
    cluster_rows = FALSE, 
    cluster_columns = FALSE,
    row_title = NULL,
    tax_anno = taxAnnotation(
      InList = ComplexHeatmap::anno_points(In_list_species, which = "row", gp= gpar(col = "red")),
      Prev. = anno_tax_prev(bar_width = 0.5, size = grid::unit(1, "cm"), border = F),
      Prop_Abd. = anno_tax_box(size = unit(2, "cm"))
      ),
    sample_anno = sampleAnnotation(
      year = anno_sample_cat("year", col = cols[1:4], legend_title = "year"),
      person = anno_sample_cat("person", col = cols[5:13], legend_title = "person"),
      type = anno_sample_cat("sample_type", col = cols[14:16], legend_title = "ctrl type")
    )
  ) %>% 
  ComplexHeatmap::draw(
  annotation_legend_list = attr(. , "AnnoLegends")
)
```

### By Year

```{r}

comp_heatmap_by_Year <- function(pseq, s_year, n_taxa = 30){
  pseq <- prune_samples(sample_data(pseq)$year == s_year, pseq)
  Most_prev_30_species <- pseq %>% 
    tax_top(n=n_taxa, by = "prev", rank = "species", undetected = 5)
  In_list_species <- lapply(Most_prev_30_species, function(x){
    genus_name <- strsplit(x, "\\s+")[[1]][1]
    return(genus_name %in% Eisenhofer_tab$genus)
  }) %>% unlist()
  selected_samples <- sample_names(pseq)[sample_data(pseq)$year == s_year]
   plt <- pseq %>% 
    tax_transform(trans = "compositional", rank = "species") %>% 
    comp_heatmap(
      #samples = selected_samples,
      taxa = Most_prev_30_species,
      cluster_rows = FALSE, 
      cluster_columns = FALSE,
      row_title = NULL,
      tax_anno = taxAnnotation(
        InList = ComplexHeatmap::anno_points(In_list_species, which = "row", gp= gpar(col = "red")),
        Prev. = anno_tax_prev(bar_width = 0.5, size = grid::unit(1, "cm"), border = F),
        Prop_Abd. = anno_tax_box(size = unit(2, "cm"))
      ),
      sample_anno = sampleAnnotation(
        #year = anno_sample_cat("year", col = cols[1:4], legend_title = "year"),
        person = anno_sample_cat("person", col = cols[5:13], legend_title = "person"),
        type = anno_sample_cat("sample_type", col = cols[14:16], legend_title = "ctrl type")
    )
  )
  return(plt)
}
## 20 most prevalence taxa at genus level
selected_year <- "2024"

pseq %>% 
  comp_heatmap_by_Year(selected_year, 20) %>% 
  ComplexHeatmap::draw(
  annotation_legend_list = attr(. , "AnnoLegends")
)

```

## Composition

```{r}
pseq %>% 
  tax_transform(trans = "compositional", rank = "genus") %>% 
  ps_mutate(
    alias = paste("ctrl", 1:nsamples(.), collapse = ":"),
    year = factor(year),
    sample_type = factor(sample_type, levels = c("buffer_ctrl", "paraffin_ctrl", "pcr_ctrl"))) %>% 
  comp_barplot(
    tax_level = "genus",
    n_taxa = 15,
    bar_width = 0.7, 
    #x = NULL,
    label = "alias",
    merge_other = FALSE, bar_outline_colour = "grey25"
  ) +
  facet_grid(
    cols = vars(sample_type), rows = vars(person),
    scales = "free_y", # this only frees y scale per row in grid faceting
    space = "free_y" # allows bars to be same size by freeing facet heights
  ) +
  scale_x_discrete(limits = rev) + # reverses order: top-down alphabetical
  coord_flip()
```

### Compositional average across sample types

```{r}
pseq %>%
  ps_select(person, year) %>% # avoids lots of phyloseq::merge_samples warnings
  phyloseq::merge_samples(group = "person") %>%
  comp_barplot(tax_level = "genus", n_taxa = 15, bar_width = 0.8) +
  coord_flip() + labs(x = NULL, y = NULL)
```

## Correlation

```{r}
## organize sample data
pseq_cor <- pseq %>% 
  ps_mutate(
    person_id = recode(person, AS=1, CD=2, CH=3, CT=4, J=5, N=6, TR=7, U=8, Unknown=9),
    ctrl_type = recode(sample_type, buffer_ctrl=1, paraffin_ctrl=2, pcr_ctrl=3),
    year_id = as.integer(year)
  )
#sample_data(pseq_cor) <- sample_data(pseq_cor)[, c("year", "person", "sample_type")]
pseq_cor %>% 
  tax_transform(trans = "compositional", rank = "genus") %>% 
  cor_heatmap(
    taxa = Most_prev_30_genus,
    vars = c("year_id", "person_id", "ctrl_type"),
    cor = "spearman"
    #tax_anno = taxAnnotation(
    #Prev. = anno_tax_prev(bar_width = 0.5, size = grid::unit(1, "cm"), border = ),
    #Abun. = anno_tax_box(size = unit(2, "cm"))
  #)
  )
```

```{r}
## manually calc using corrr package
X <- pseq_cor %>% sample_data() %>% as_tibble() %>% select(year_id, person_id, sample_type)
X$year <- as.factor(X$year)
X$person <- as.factor(X$person)
X$sample_type <- as.factor(X$sample_type)

Y <- pseq_cor %>% tax_transform(trans = "compositional", rank = "species") %>% otu_table() %>% as_tibble()
library(corrr)
corrr::correlate(X, Y, method = "spearman")
```

test

```{r}
pml <- pseq %>% 
  tax_glom(taxrank = "genus") %>% 
  transform_sample_counts(function(x) {x/sum(x)}) %>% 
  ps_select(year, person, sample_type) %>% 
  ps_melt() %>% 
  arrange(OTU) 

pml <- pml %>% 
  select(-species) %>% 
  mutate(Log10.Abund = log10(Abundance + 1e-7))

## add prevalence grouped by year
pseq_genus <- pseq %>% 
  tax_glom(taxrank = "genus")
pseq_2021_prev <- pseq_genus %>% 
  prune_samples(sample_data(.)$year == "2021", .) %>% 
  prevalence()
pseq_2022_prev <- pseq_genus %>% 
  prune_samples(sample_data(.)$year == "2022", .) %>% 
  prevalence()
pseq_2023_prev <- pseq_genus %>% 
  prune_samples(sample_data(.)$year == "2023", .) %>% 
  prevalence()
pseq_2024_prev <- pseq_genus %>% 
  prune_samples(sample_data(.)$year == "2024", .) %>% 
  prevalence()

library(tibble)
df_prev <- cbind(pseq_2021_prev, pseq_2022_prev, pseq_2023_prev, pseq_2024_prev)
colnames(df_prev) <- c("2021", "2022", "2023", "2024")


df_prev_long <- df_prev %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "OTU") %>% 
  pivot_longer(cols = !OTU,
               names_to = "year",
               values_to = "Prevalence")

taxa_genus <- "Bacillus"
ylim.prim <- c(-7, 0)   # in this example, Log10 rel abun
ylim.sec <- c(0, 1)    # in this example, Prev
b <- diff(ylim.prim)/diff(ylim.sec)
a <- ylim.prim[1] - b*ylim.sec[1]

pml %>% 
  left_join(., df_prev_long, by = c("OTU", "year")) %>% 
  filter(genus == taxa_genus) %>% 
  ggplot(mapping = aes(x = year))+
  #geom_boxplot(aes(y = Abundance)) +
  geom_boxplot(aes(y = Log10.Abund)) +
  geom_point(aes(y =a + b*Prevalence), color = "red", size = 2) +
  geom_line(aes(y =a + b*Prevalence), color = "gray", linewidth = 1) +
  scale_y_continuous(
    # Features of the first axis
    name = "Log10 Rel. Abund",
    # Add a second axis and specify its features
    sec.axis = sec_axis(~ (. - a)/b, name="Prev.")
  )+
  ggtitle(taxa_genus)
```
